Python as a machine learning language: experiences from the \sklearn project

### 2013-06-10 paper.tex
attributes -> features per scikit-learn convention
Attributes is ambiguous in Python context.

In most machine learning tasks, data is modeled as a set of variables.  For
example, in a classification or regression task, the goal is to find a mapping
between input variables $X_1, ..., X_p$ -- called attributes or features -- and
some output variable $Y$. A sample is then defined as a tuple of values $([x_1,
..., x_p]^\mathrm{T}, y)$ of these variables and a dataset as a collection of
such samples.  As such, matrices of numerical values constitute a natural and
widely used representation in machine learning. In this view, each row in the
matrix then corresponds to a sample of the dataset and each column to one of the
variables of the problem.

@@

In \sklearn, classical learning algorithms are not the only objects
to be implemented as estimators. For example, preprocessing routines (e.g.,
vectorization of text documents, scaling of attributes, etc) or feature
extraction techniques also implement the same interface. Even those estimators
that are entirely stateless and therefore do not require the \texttt{fit} method
to perform any useful work implement the estimator interface. As we will
illustrate in the next sections, this design pattern is indeed of prime
importance for consistency, composition and parameter validation reasons.

>>>>

In most machine learning tasks, data is modeled as a set of variables.  For
example, in a classification or regression task, the goal is to find a mapping
between input variables $X_1, ..., X_p$, called features, and
some output variable $Y$. A sample is then defined as a tuple of values $([x_1,
..., x_p]^\mathrm{T}, y)$ of these variables and a dataset as a collection of
such samples.  As such, matrices of numerical values constitute a natural and
widely used representation in machine learning. In this view, each row in the
matrix then corresponds to a sample of the dataset and each column to one of the
variables of the problem.

@@

In \sklearn, classical learning algorithms are not the only objects
to be implemented as estimators. For example, preprocessing routines (e.g.,
vectorization of text documents, scaling of features, etc) or feature
extraction techniques also implement the same interface. Even those estimators
that are entirely stateless and therefore do not require the \texttt{fit} method
to perform any useful work implement the estimator interface. As we will
illustrate in the next sections, this design pattern is indeed of prime
importance for consistency, composition and parameter validation reasons.
